High-Throughput Phenotyping using Computer Vision and Machine Learning \\ \large SMC Data Challenge \#1

### 2023-07-29 paper/main.tex
updated everythin

\makeatletter
\def\ps@pprintTitle{%
  \let\@oddhead\@empty
  \let\@evenhead\@empty
  \let\@oddfoot\@empty
  \let\@evenfoot\@oddfoot
}
\makeatother

@@

@@

\author[]{Vivaan Singhvi}
\author[]{Langalibalele Lunga}
\author[]{Pragya Nidhi}
\author[]{Chris Keum}
\author[]{Varrun Prakash}

@@

In the second part of challenge 4, we aimed to find a correlation between phenotypes and environmental features, such as soil type and weather conditions. Using the EXIF tags, we were able to retrieve the coordinates where the image was taken. We noticed all of the images contained were taken in approximately the same two locations, so any weather or soil API would be unable to provide specific conditions. If we were given this information as part of the dataset, we would have been better able to find correlations. Regardless, a study on how the temperature affects the phenotype and development plasticity in Arabidopsis Thaliana \citep{ibanez2017ambient} placed the plants in different temperature environments in order to measure their differences. If we had more information regarding the conditions in which the plants were raised, we would be better able to determine if there was a correlation between phenotypes and environment.

@@

We would like to thank Dr. Ty Frazier for his suggestions and mentoring throughout this project.

>>>>

@@

\journal{SMCDC23}
\renewcommand*{\today}{July 28, 2023}

@@

\author[fhs]{Vivaan Singhvi}
\author[fhs]{Langalibalele Lunga}
\author[fhs]{Pragya Nidhi}
\author[fhs]{Chris Keum}
\author[fhs]{Varrun Prakash}

\affiliation[fhs]{organization={Farragut High School},
            addressline={11237 Kingston Pike},
            city={Knoxville},
            postcode={37922},
            state={Tennesee},
            country={United States}}

@@

In the second part of challenge 4, we aimed to find a correlation between phenotypes and environmental features, such as soil type and weather conditions. Using the EXIF tags, we were able to retrieve the coordinates where the image was taken. We noticed all of the images contained were taken in approximately the same location, so any weather or soil API would be unable to provide specific conditions. If we were given this information as part of the dataset, we would have been better able to find correlations. Regardless, a study on how the temperature affects the phenotype and development plasticity in Arabidopsis Thaliana \citep{ibanez2017ambient} placed the plants in different temperature environments in order to measure their differences. If we had more information regarding the conditions in which the plants were raised, we would be better able to determine if there was a correlation between phenotypes and environment.

@@

We thank Dr. Ty Frazier at Oak Ridge National Laboratory for his helpful suggestions and mentoring throughout this project.
